---
title: "R Version"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
```
```{r}
library(tidytable)
```

```{r}

# download.file("https://raw.githubusercontent.com/JovianML/opendatasets/master/data/stackoverflow-developer-survey-2020/survey_results_schema.csv", "survey_results_schema.csv")
```


```{r}
# download.file("https://raw.githubusercontent.com/JovianML/opendatasets/master/data/stackoverflow-developer-survey-2020/survey_results_public.csv", "survey_results_public.csv")
```

```{r}
# download.file("https://raw.githubusercontent.com/JovianML/opendatasets/master/data/stackoverflow-developer-survey-2020/README.txt", "README.txt")
```

```{r}
survey_raw_df <- read_csv("survey_results_public.csv")
```
```{r}
survey_raw_df
```
```{r}
schema_raw_df <- read_csv("survey_results_schema.csv")
schema_raw_df
```
```{r}
str(schema_raw_df)
```
```{r}
schema_raw_df[1]
```
```{r}
ind <- schema_raw_df$Column == "YearsCodePro"
schema_raw_df$QuestionText[ind]
```
```{r}
selected_columns <- c("Country", "Age", "Gender", "EdLevel", "UndergradMajor",
                      "Hobbyist", "Age1stCode", "YearsCode", "YearsCodePro",
                      "LanguageWorkedWith", "LanguageDesireNextYear", 
                      "NEWLearn", "NEWStuck", "Employment", "DevType", 
                      "WorkWeekHrs", "JobSat", "JobFactors",
                      "NEWOvertime", "NEWEdImpt")
length(selected_columns)
```
```{r}
survey_df <- survey_raw_df %>%
  select(all_of(selected_columns))
```

```{r}
ind <- which(schema_raw_df$Column %in% selected_columns)
schema <- schema_raw_df[ind,]
schema
```

```{r}
str(survey_df)
```
```{r}
survey_df |>
  mutate(
    Age1stCode = as.numeric(Age1stCode),
    YearsCode = as.numeric(YearsCode),
    YearsCodePro = as.numeric(YearsCodePro)
  ) -> survey_df
str(survey_df)
```
```{r}
summary(survey_df)
```

```{r}
survey_df |>
  summarise(Age = n(), .by = Gender)
```


```{r}
survey_df |>
  filter(Age >= 10 | is.na(Age)) |>
  filter(WorkWeekHrs <= 140 | is.na(WorkWeekHrs)) |>
  summarise(Age = n(), .by = Gender)
```

```{r}
survey_df %>% 
  mutate(Gender = if_else(grepl(";", Gender), NA, Gender)) -> survey_df
```

```{r}
survey_df |>
  summarise(Age = n(), .by = Gender)
```

```{r}
survey_df |> sample(10)
```

## Exploratory Analysis and Visualization

Before we ask questions about the survey responses, it would help to understand the respondents' demographics, i.e., country, age, gender, education level, employment level, etc. It's essential to explore these variables to understand how representative the survey is of the worldwide programming community. A survey of this scale generally tends to have some selection bias.

### Country

Let's look at the number of countries from which there are responses in the survey and plot the ten countries with the highest number of responses.

```{r}
ind_country <- schema$Column == "Country"
schema$QuestionText[ind_country]
```
```{r}
country_question <- schema$QuestionText[schema$Column == "Country"]
```
```{r}
length(unique(survey_df$Country))
```
```{r}
survey_df |>
  summarise(Count = n(), .by = Country) |>
  top_n(n = 15, wt = Count) |>
  mutate(Country = reorder(Country, Count, decreasing = TRUE)) -> top_countries
top_countries
```

```{r}
top_countries |>
  ggplot(aes(x = Country, y = Count, fill = Country)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  ggtitle(country_question) +
  theme(axis.text.x = element_text(angle=75, vjust=1, hjust = 1))
```

```{r}
survey_df |>
  ggplot(aes(Age)) +
  geom_histogram(binwidth = 5, colour = "black", fill="purple") +
  scale_x_continuous(name = "Age",
                   breaks = seq(10, 80, 10)) +
  xlim(10, 80) +
  ylab("Number of respondents")
```

It appears that a large percentage of respondents are 20-45 years old. It's somewhat representative of the programming community in general. Many young people have taken up computer science as their field of study or profession in the last 20 years.

Exercise: You may want to filter out responses by age (or age group) if you'd like to analyze and compare the survey results for different age groups. Create a new column called AgeGroup containing values like Less than 10 years, 10-18 years, 18-30 years, 30-45 years, 45-60 years and Older than 60 years. Then, repeat the analysis in the rest of this notebook for each age group.

```{r}
survey_df |>
  mutate(AgeGroup = case_when(
    Age < 18 ~ "Younger than 18",
    Age >= 18 & Age <= 25 ~ "18-25 years",
    Age > 25 & Age <= 35 ~ "26-35 years",
    Age > 35 & Age <= 45 ~ "36-45 years",
    Age > 45 & Age <= 55 ~ "46-55 years",
    TRUE ~ "Older than 55"
  )) -> survey_agegroup_df
survey_agegroup_df
```

```{r}
survey_df |>
  na.omit() |>
  summarise(Age = n(), .by = Gender)
```

```{r}
survey_df |>
  drop_na() |>
  summarise(Age = n(), .by = Gender) |>
  mutate(Percentage = Age / sum(Age)) |>
  mutate(labels = scales::percent(Percentage)) -> survey_df_percent_age
survey_df_percent_age |>
  ggplot(aes(x="", y=Percentage, fill = Gender)) +
	geom_col() +
	coord_polar(theta = "y") +
  geom_text(aes(label = labels), position = position_stack(vjust = 0.5)) +
  theme(axis.text=element_blank(), 
        axis.ticks = element_blank(), 
        panel.grid  = element_blank()) +
  xlab("") +
  ylab("Percentage of responses")
```



























