---
title: "R Version"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
```
```{r}
library(tidytable)
```

```{r}

# download.file("https://raw.githubusercontent.com/JovianML/opendatasets/master/data/stackoverflow-developer-survey-2020/survey_results_schema.csv", "survey_results_schema.csv")
```


```{r}
# download.file("https://raw.githubusercontent.com/JovianML/opendatasets/master/data/stackoverflow-developer-survey-2020/survey_results_public.csv", "survey_results_public.csv")
```

```{r}
# download.file("https://raw.githubusercontent.com/JovianML/opendatasets/master/data/stackoverflow-developer-survey-2020/README.txt", "README.txt")
```

```{r}
survey_raw_df <- read_csv("survey_results_public.csv")
```
```{r}
survey_raw_df
```
```{r}
schema_raw_df <- read_csv("survey_results_schema.csv")
schema_raw_df
```
```{r}
str(schema_raw_df)
```
```{r}
schema_raw_df[1]
```
```{r}
ind <- schema_raw_df$Column == "YearsCodePro"
schema_raw_df$QuestionText[ind]
```
```{r}
selected_columns <- c("Country", "Age", "Gender", "EdLevel", "UndergradMajor",
                      "Hobbyist", "Age1stCode", "YearsCode", "YearsCodePro",
                      "LanguageWorkedWith", "LanguageDesireNextYear", 
                      "NEWLearn", "NEWStuck", "Employment", "DevType", 
                      "WorkWeekHrs", "JobSat", "JobFactors",
                      "NEWOvertime", "NEWEdImpt")
length(selected_columns)
```
```{r}
survey_df <- survey_raw_df %>%
  select(all_of(selected_columns))
```

```{r}
ind <- which(schema_raw_df$Column %in% selected_columns)
schema <- schema_raw_df[ind,]
schema
```

```{r}
str(survey_df)
```
```{r}
survey_df |>
  mutate(
    Age1stCode = as.numeric(Age1stCode),
    YearsCode = as.numeric(YearsCode),
    YearsCodePro = as.numeric(YearsCodePro)
  ) -> survey_df
str(survey_df)
```
```{r}
summary(survey_df)
```
```{r}
# survey_df |>
#  filter(Age >= 10 & Age <= 100) |>
#  filter(WorkWeekHrs <= 140) -> survey_df
```

```{r}
survey_df |>
  summarise(Age = n(), .by = Gender)
```


```{r}
survey_df |>
  filter(Age >= 10 | is.na(Age)) |>
  filter(WorkWeekHrs <= 140 | is.na(WorkWeekHrs)) |>
  summarise(Age = n(), .by = Gender)
```

```{r}
survey_df %>% 
  mutate(Gender = if_else(grepl(";", Gender), NA, Gender)) -> survey_df
```

```{r}
survey_df |>
  summarise(Age = n(), .by = Gender)
```

```{r}
survey_df |> sample(10)
```

## Exploratory Analysis and Visualization

Before we ask questions about the survey responses, it would help to understand the respondents' demographics, i.e., country, age, gender, education level, employment level, etc. It's essential to explore these variables to understand how representative the survey is of the worldwide programming community. A survey of this scale generally tends to have some selection bias.

### Country

Let's look at the number of countries from which there are responses in the survey and plot the ten countries with the highest number of responses.

```{r}
ind_country <- schema$Column == "Country"
schema$QuestionText[ind_country]
```
```{r}
country_question <- schema$QuestionText[schema$Column == "Country"]
```
```{r}
length(unique(survey_df$Country))
```
```{r}
survey_df |>
  summarise(Count = n(), .by = Country) |>
  top_n(n = 15, wt = Count) |>
  mutate(Country = reorder(Country, Count, decreasing = TRUE)) -> top_countries
top_countries
```

```{r}
top_countries |>
  ggplot(aes(x = Country, y = Count, fill = Country)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  ggtitle(country_question) +
  theme(axis.text.x = element_text(angle=75, vjust=1, hjust = 1))
```

```{r}
survey_df |>
  ggplot(aes(Age)) +
  geom_histogram(binwidth = 5, colour = "black", fill="purple") +
  scale_x_continuous(name = "Age",
                   breaks = seq(10, 80, 10)) +
  xlim(10, 80) +
  ylab("Number of respondents")
```



































